Supplement to: Learning to Infer Graphics Programs from Hand-Drawn Images

### 2017-05-19 supplement.tex
lots of changes and now it needs to be smaller

\title{Supplement to: Inferring Graphics Programs from Images}

@@

>>>>

\title{Supplement to: Learning to Infer Graphics Programs from Hand-Drawn Images}

@@

\section{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
The program synthesizer can help correct errors from the execution trace proposal network by favoring execution traces which lead to more concise or general programs.
For example, one generally prefers figures with perfectly aligned objects over figures whose parts are slightly misaligned -- and precise alignment lends itself to short programs.
Similarly, figures often have repeated parts,
which the program synthesizer might be able to model as a loop or reflectional symmetry.
So, in considering several candidate traces proposed by the neural network,
we might prefer traces whose best programs have desirable features such being short or having iterated structures.

Concretely, we implemented the following scheme: for an image $I$, the neurally guided sampling scheme of section~\ref{neuralNetworkSection} samples a set of candidate traces, written $\mathcal{F}(I)$.
Instead of predicting the most likely trace in $\mathcal{F}(I)$ according to the neural network,
we can take into account the programs that best explain the traces. 
Writing $\hat{T}(I)$ for the trace the model predicts for image $I$,
\begin{equation}
\hat{T}(I) = \argmax_{T\in \mathcal{F}(I)} L_{\text{learned}}(I | \text{render}(T))\times \probability_\theta[T|I] \times\probability_{\beta} [ \text{program}(T)] 
\end{equation}
where $\probability_{\beta} [\cdot]$ is a prior probability
distribution over programs parameterized by $\beta$.
This is equivalent to doing
MAP inference in a generative model where the program is first drawn
from $\probability_{\beta} [\cdot]$, then the program is executed deterministically,
and then we observe a noisy version of the program's output, where $L_\text{learned}(I|\text{render}(\cdot))\times\probability_\theta[\cdot|I]$
is our observation model.

Given a corpus of graphics program synthesis problems with annotated ground truth traces (i.e. $(I,T)$ pairs),
we find a maximum likelihood estimate of $\beta$:
\begin{equation}
  \beta^* = \argmax_{\beta} \expect \left[ \log \frac{\probability_{\beta} [\text{program}(T)]\times L_{\text{learned}}(I|\text{render}(T))\times \probability_\theta[T|I]}{\sum_{T'\in \mathcal{F}(I)} \probability_{\beta} [\text{program}(T')]\times L_{\text{learned}}(I|\text{render}(T'))\times \probability_\theta[T'|I]} \right]
\end{equation}
where the expectation is taken both over the model predictions and the
$(I,T)$ pairs in the training corpus.  We define $\probability_{\beta}
[\cdot]$ to be a log linear distribution $\propto \exp
(\beta\cdot \phi(\text{program}))$, where $\phi(\cdot)$ is a feature
extractor for programs.  We extract a few basic features of a
program, such as its size and how many loops it has, and use these
features to help predict whether a trace is the correct explanation
for an image.

We synthesized programs for the top 10 traces
output by the deep network.  Learning this prior over programs can
help correct mistakes made by the neural network, and also
occasionally introduces mistakes of its own; see
Fig.~\ref{exampleOfProgramCorrectingMistake} for a representative
example of the kinds of corrections that it makes. On the whole
it modestly improves our Top-1 accuracy from 58\% to 61\%.  Recall that
from Fig. 6 of the main paper that the best improvement
in accuracy we could possibly get is 65\% by looking at the top 10 traces. 
\begin{wrapfigure}{R}{5.5cm}
  \includegraphics[width = 5cm]{figures/programSuccess7.png}
  \caption{Left: hand drawing. Center: interpretation favored by the deep network. Right: interpretation favored after learning a prior over programs. Our learned prior favors shorter, simpler programs, thus continuing the pattern of not having an arrow is preferred.}\label{exampleOfProgramCorrectingMistake}
\end{wrapfigure}
